Ashley Lagrou VIP Plan

### 2020-05-08 Ashley Lagrou VIP timeline.Rmd
Stuff for ashley
cleaning up

Plotting is an important first step to understanding your data. It should always be your first stop once you have clean data in hand.

We will be using the ggplot2 package in R for all of our plotting
```{r}
library(ggplot2)
```

>>>>

We will use the package ggplot2 to plot the data that you have collected/extrapolated.

If you remember from before, the ggplot() function follows the [grammar of graphics](https://towardsdatascience.com/a-comprehensive-guide-to-the-grammar-of-graphics-for-effective-visualization-of-multi-dimensional-1f92b4ed4149), a theory for how to visualize data that relies on stacking layers on top of each other.

When you create ggplot() code, the top most code will be the first layer created. For our purposed, we will always want this to be the axes of the figure. We will do this by specifying the data and the x and y axes. Remember that the x and y axes need to be wrapped in an aestetic function aes(). This just tells ggplot to look for these things in the dataset that we specified.

```{r}
library(ggplot2) #load the package

ggplot(data= dat, aes(x=GeogDistModel,y=BoilTime))

You'll see that this just "sets the stage" for the rest of the plot. We haven't told it what kind of plot we want yet.

Next, we will layer the data on top of this background.

```{r}
ggplot(data= dat, aes(x=GeogDistModel,y=BoilTime))+
  geom_point()
```

Is this the best way to visualize this simple dataset? probably not. Can you think of  better way?

There is a ton of flexibility in ggplot2. See if you can make this plot better.

Once you do that, see if you can plot your data that you created by extrapolating from the fee data we had.

I like to hand draw my plots first so I know what I'm aiming for.

If you want help and inspiration check out the [Cookbook for ggplot](http://www.cookbook-r.com/Graphs/) and the [ggplot gallery](https://www.r-graph-gallery.com/).
